Turtlebot SLAM

### 2013-01-22 Article/Article.tex
Removed the line referring to the project
Added scanmatch figure and described.

\begin{abstract}
To perform an assignment a robot needs a map of the environment, an added difficulty could be that the robot needs to build this map on his own. The task of mapping an environment can be split into two main components, namely exploration and SLAM which stands for Simultaneous Localization And Mapping. Exploration is based on the idea of frontiers, these are regions which separate unexplored space from free explored space, and a strategy determines to which frontier the robot moves next. SLAM incorporates the new data as it becomes available. One intuitive way is to represent all the data as a graph and then try to find a configuration of nodes which is maximally consistent with the constraints. This article will describe an implementation of this so called GraphSLAM with frontier exploration. All the implemented code is first tested and validated in a simulator and later run on a real robot, a TurtleBot.

This article accompanies the research project "TurtleBot SLAM" from the Master "Artificial Intelligence" of Maastricht University.
\end{abstract}

@@

>>>>

\begin{abstract}
To perform an assignment a robot needs a map of the environment, an added difficulty could be that the robot needs to build this map on his own. The task of mapping an environment can be split into two main components, namely exploration and SLAM which stands for Simultaneous Localization And Mapping. Exploration is based on the idea of frontiers, these are regions which separate unexplored space from free explored space, and a strategy determines to which frontier the robot moves next. SLAM incorporates the new data as it becomes available. One intuitive way is to represent all the data as a graph and then try to find a configuration of nodes which is maximally consistent with the constraints. This article will describe an implementation of this so called GraphSLAM with frontier exploration. All the implemented code is first tested and validated in a simulator and later run on a real robot, a TurtleBot.
\end{abstract}

@@

Figure \ref{fig:scanmatcher} shows the robot in its current position (left) and the result of matching the previous scan to the current scan (right). The robot rotated slightly clockwise. The red point cloud represents the detected obstacles before the rotation when the robot was still standing parallel to the wall. The green point cloud represents the current laser scan. The scan matching algorithm then calculates the most likely transformation between these two point clouds and applies this transformation to the previous scan, resulting in the purple point cloud.

\begin{figure}[htbp]
	\centering
		\includegraphics[width=0.45\textwidth]{figures/Scanmatch.jpg}
	\caption{Previous scan matched with the current scan}
	\label{fig:scanmatcher}
\end{figure}
